Modern Graph Generators: A Survey

### 2018-11-09 generators_LinkedData.tex
rewriting pages 9-10 (iThenticate)

\paragraph{LUBM} The use-case driven Lehigh University Benchmark (LUBM)\footnote{\url{http://swat.cse.lehigh.edu/projects/lubm/}} considers the university domain. The ontology defines 43 classes and 32 properties, including 25 object properties and 7 datatype properties~\cite{Guo2005158}. The LUBM benchmark also provides 14 test queries. The authors focus on \emph{extensional} queries, i.e., queries about the instance data over ontologies, as an opposite to \emph{intentional} queries (i.e., queries about classes and properties). The Univ-Bench Artificial  (UBA) data generator features random and repeatable data generation (exploiting classical linear congruential generator, LCG, of numbers). In particular, data generated by the tool are exactly repeatable with respect to universities (assigning them zero-based indexes, i.e., the first university is named University0 and so on).  The generator allows a user to specify the seed for random number generation, the number of universities, and the starting index of the universities.

An extension of LUBM, the Lehigh BibTeX Benchmark (LBBM)~\cite{Wang2005}, enables generating synthetic data for different ontologies. The generation is divided into two phases: (1) the property-discovering phase, and (2) the data generation phase. The authors present a probabilistic model that, given representative data of some domain, can capture the properties of the data and generate synthetic data that has similar properties. A Monte Carlo algorithm is used to generate synthetic data. The approach is demonstrated on the Lehigh University BibTeX ontology which consists of 28 classes and 80 properties. 12 test queries were designed for  the benchmark data. Another extension of LUBM, the University Ontology Benchmark (UOBM)\footnote{\url{https://www.cs.ox.ac.uk/isg/tools/UOBMGenerator/}}, focuses on two aspects: (1) usage of all constructs of OWL Lite and OWL DL~\cite{owl} and (2) lack of necessary links between the generated data which thus form isolated graphs~\cite{Ma:2006:TCO:2094613.2094629}. In the former case the original ontology is replaced by the two types of extended versions from which the user can choose. In the latter case cross-university and cross-department links are added to create a more complex graph.

@@

\paragraph{BSBM} The Berlin SPARQL Benchmark (BSBM)\footnote{\url{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}}, models an e-commerce domain where types Product, Offer and Vendor are used to model the relationships between products and the vendors offering them, while types Person and Review are used to model the relationship between users and product reviews these users write~\cite{Bizer09theberlin}.
The benchmark comes with 12 queries and 2 query mixes (sequences of the 12 queries) emulating the search and navigation pattern of a consumer looking for a product. The data generator supports the creation of arbitrarily large datasets using the number of products $n$ as scale factor which further influences also other characteristics of the data, such as, e.g., the depth of type hierarchy of products (defined as $d = round(log_{10}(n))/2 + 1$), branching factor ($bfr = 2 \times round(log_{10}(n))$), the number of product features (having $lowerBound = 35 \times i / (d \times (d+1)/2 - 1)$ and $upperBound = 75 \times i / (d \times (d+1)/2 - 1)$) etc. BSBM can output two representations -- an RDF representation and a purely relational representation. Thus, BSBM also defines an SQL~\cite{sql} representation of the queries. This allows comparison of SPARQL~\cite{sparql} results  to be compared against the performance of traditional RDBMSs.

>>>>

\paragraph{LUBM} The use-case driven Lehigh University Benchmark (LUBM)\footnote{\url{http://swat.cse.lehigh.edu/projects/lubm/}} considers the university domain. The ontology defines 43 classes and 32 properties, including 25 object properties and 7 datatype properties~\cite{Guo2005158}. The LUBM benchmark also provides 14 test queries. The authors focus on \emph{extensional} queries, i.e., queries about the instance data over ontologies, as an opposite to \emph{intentional} queries (i.e., queries about classes and properties). The Univ-Bench Artificial  (UBA) data generator features random and repeatable data generation (exploiting classical linear congruential generator, LCG, of numbers). In particular, data generated by the tool are assigned zero-based indexes (i.e., the first university is named University0 and so on), thus they are reproducible at any time with the same indexes.  The generator allows to specify a seed for random number generation, along with the desired number of universities, and the starting index of the universities.

An extension of LUBM, the Lehigh BibTeX Benchmark (LBBM)~\cite{Wang2005}, enables generating synthetic data for different ontologies. The generation is divided into two phases: (1) the property-discovering phase, and (2) the data generation phase. The authors present a probabilistic model that can emulate the properties of the data of a particular domain and generate synthetic data exhibiting similar properties. A Monte Carlo algorithm is employed to output synthetic data. The approach is demonstrated on the Lehigh University BibTeX ontology which consists of 28 classes along with 80 properties. The LUBM benchmark includes 12 test queries that were designed for the benchmark data. Another extension of LUBM, the University Ontology Benchmark (UOBM)\footnote{\url{https://www.cs.ox.ac.uk/isg/tools/UOBMGenerator/}}, focuses on two aspects: (1) usage of all constructs of OWL Lite and OWL DL~\cite{owl} and (2) lack of necessary links between the generated data which thus form isolated graphs~\cite{Ma:2006:TCO:2094613.2094629}. In the former case the original ontology is replaced by the two types of extended versions from which the user can choose. In the latter case cross-university and cross-department links are added to create a more complex graph.

@@

\paragraph{BSBM} The Berlin SPARQL Benchmark (BSBM)\footnote{\url{http://wifo5-03.informatik.uni-mannheim.de/bizer/berlinsparqlbenchmark/}}, models an e-commerce domain where types Product, Offer and Vendor are used to model the relationships between products and the vendors offering them, while types Person and Review are used to model the relationship between users and product reviews these users write~\cite{Bizer09theberlin}.
The benchmark comes equipped with 12 queries and 2 query mixes (sequences of the 12 queries) emulating the search and navigation pattern of a consumer looking for a product. The data generator supports the creation of arbitrarily large datasets using the number of products $n$ as scale factor which further influences also other characteristics of the data, such as, e.g., the depth of type hierarchy of products (defined as $d = round(log_{10}(n))/2 + 1$), branching factor ($bfr = 2 \times round(log_{10}(n))$), the number of product features (having $lowerBound = 35 \times i / (d \times (d+1)/2 - 1)$ and $upperBound = 75 \times i / (d \times (d+1)/2 - 1)$) etc. BSBM can output two representations -- an RDF representation and a purely relational representation. Thus, BSBM also defines an SQL~\cite{sql} representation of the queries. This allows comparison of SPARQL~\cite{sparql} results  to be compared against the performance of traditional RDBMSs.

### 2018-11-09 generators_general.tex
rewriting pages 9-10 (iThenticate)

\paragraph {R-MAT} R-MAT (\emph{R}ecursive \emph{Mat}rix) is a procedural synthetic graph generator which is designed to generate power-law degree
distributions~\cite{DBLP:conf/sdm/ChakrabartiZF04}.
The generator is recursive and uses only a small number of parameters.
In principle, the strategy of this generator is to find simple mechanisms to generate graphs that match
the properties of the real graphs. In particular, the design goals of R-MAT is to generate graphs that match the degree distributions, imitate a community structure and have a small diameter. R-MAT can generate weighted, directed and bipartite graphs.

\paragraph{GraphGen} For the purpose of testing the scalability of an indexing
technique called FG-index~\cite{Cheng:2007:FTV:1247480.1247574} on the size of the
database of graphs, their average size and average density, the authors have
also implemented a synthetic generator called
GraphGen\footnote{https://www.cse.ust.hk/graphgen/}. It is
based on the IBM synthetic data generation code for associations and sequential
patterns\footnote{From 1996, no longer available at
\url{http://www.almaden.ibm.com/cs/projects/iis/hdb/Projects/data
mining/mining.shtml}}. GraphGen creates a collection of labeled, undirected and
connected graphs which focuses on the performance evaluation of frequent subgraph mining
algorithms and graph query processing algorithms. The result is represented as a
list of graphs, each consisting of a list of nodes and a list of edges.

@@

\paragraph{Darwini} Darwini~\cite{edunov2016darwini} is an extension of BTER
designed to run on Vertex Centric computing frameworks like
Pregel~\cite{malewicz2010pregel} or Apache Giraph~\cite{ching2015one}, with the
additional feature that it is more accurate when reproducing the clustering
coefficient of the input graph. Instead of just focusing on the average
clustering coefficient for each degree, Darwini is able to model the clustering
coefficient distribution per degree. It achieves this by grouping the vertices
of the graph into buckets by the expected number of closed triangles that they need
to close in order to attain the expected clustering coefficient, which is
sampled from the input distributions. Then, the vertices in each bucket are
connected randomly with a probability that would produce the expected
desired number of triangles for such bucket. Then, as in BTER, the excess degree
is used to connect the different buckets. The authors report that Darwini is
able to generate graphs with billions and even trillions of edges.

>>>>

\paragraph {R-MAT} R-MAT (\emph{R}ecursive \emph{Mat}rix) is a procedural synthetic graph generator which is designed to generate power-law degree
distributions~\cite{DBLP:conf/sdm/ChakrabartiZF04}.
The generator is recursive and employs a fairly small number of parameters.
In principle, the strategy of this generator is to achieve simple means to generate graphs that match
the properties of the real graphs. In particular, the design goals of R-MAT is to generate graphs that match the degree distributions, imitate a community structure and have a small diameter. R-MAT can generate weighted, directed and bipartite graphs.

\paragraph{GraphGen} For the purpose of testing the scalability of an indexing
technique called FG-index~\cite{Cheng:2007:FTV:1247480.1247574} on the size of the
database of graphs, their average size and average density, the authors have
also implemented a synthetic generator called
GraphGen\footnote{https://www.cse.ust.hk/graphgen/}. It relies on data generation code for associations and sequential
patterns provided by IBM \footnote{From 1996, no longer available at
\url{http://www.almaden.ibm.com/cs/projects/iis/hdb/Projects/data
mining/mining.shtml}}. GraphGen yields a collection of undirected, labeled and
connected graphs. It addresses the performance evaluation of frequent subgraph mining
algorithms and graph query processing algorithms. The result is represented as a
list of graphs, each consisting of a list of nodes along with a list of edges.

@@

\paragraph{Darwini} Darwini~\cite{edunov2016darwini} is an extension of BTER
designed to run on Vertex Centric computing frameworks like
Pregel~\cite{malewicz2010pregel} or Apache Giraph~\cite{ching2015one}, with the
additional feature that it is more accurate when reproducing the clustering
coefficient of the input graph. Instead of just focusing on the average
clustering coefficient for each degree, Darwini is able to model the clustering
coefficient distribution per degree. It achieves this by gathering the vertices
of the graph into buckets based on the expected number of closed triangles that they need
to close in order to attain the expected clustering coefficient. The latter is
sampled from the input distributions. Then, the vertices in each bucket are
connected randomly with a probability that would produce the expected
desired number of triangles for each bucket. Then, as in BTER, the excess degree
is used to connect the different buckets. The authors report that Darwini is
able to generate graphs with billions and even trillions of edges.
